### 2018-07-08 methods.tex
github website

Saltproc is currently in active development in Github, and has unit tests and
Travis continuous integration for sustainable development. There is also documentation
generated through Sphinx document generator for ease of use. We plan to implement
user-defined reprocessing scheme definition, two-region \gls{MSR} modeling capabilities,
and decay modeling in future releases.

>>>>

Saltproc is currently in active development in Github (https://github.com/arfc/saltproc), and has unit tests and
Travis continuous integration for sustainable development. There is also documentation
generated through Sphinx document generator for ease of use. We plan to implement
user-defined reprocessing scheme definition, two-region \gls{MSR} modeling capabilities,
and decay modeling in future releases.
